---
title: "R Notebook"
output: html_notebook
---

    Titanic slip up
    
```{r}
library(gtools)
library(tidyverse)
library(janitor)
source('prob.R')

tinytonic <- read_csv("titanic.csv")
```

```{r}

  unique(tinytonic$class)
```


```{r}
tinytonic <- tinytonic %>% 
  mutate(crew = str_detect(class, "engineering crew")|str_detect(class, "deck crew")|str_detect(class, "restaurant staff")|str_detect(class, "victualling crew"))
```


```{r}
cont_table <- tinytonic %>% 
  tabyl(crew, survived)
```

```{r}
cont_table %>% 
  adorn_totals(where = c("row", "col")) %>% 
  adorn_percentages(denominator = "all")
```


checking if these losers questions are worthy of investigation 
```{r}
chisq.test(cont_table)
```
damn...


using the table we can pull all the values we need

p(survived | crew) = p(S intersect C)/p(C)
```{r}
0.09560489 / 0.4032623
```

p(survived | passenger) = p(S intersect P)/p(P)

```{r}
0.22655188 * 0.5967377
```

the calculations suggest you were more likely to survive as a crew member



    YATZHEE
    
1. 4/6 = 1/3

2. 6^3 = 216

3. 

```{r}

# table of all permutations within the event
rolling_567 <- rolldie(4) %>% 
  filter(X1 + X2 + X3 + X4 == 5|
          X1 + X2 + X3 + X4 == 6|
          X1 + X2 + X3 + X4 == 7)

#dividing n(event space) by n(sample space)

nrow(rolling_567)/nrow(rolldie(4))
```

we assume independence of all rolls, and fairness of dice

4. 5p5 = 5! = 120, so we have 1/120

5. (1/6)^6 = 2.143347e-05
    
    1/6 (nCn always = 1)
    
6. 1/2 since half the black cards are spades
      