---
title: "R Notebook"
output: html_notebook
---

```{r}
books <- read.csv('data/books.csv')

library(tidyverse)
library(janitor)

view(books)
```



first searching the dataset for any missing values
```{r}

books_na <-  tibble(books_na <- sapply(books, is.na))

summarise(books_na, 
          across(.cols = everything(),
                 .fns = ~sum(.x)
                 ))

```
going off NA's alone, there appear to be no missing entries in the data

Q: How do we look for missing entries in big data



what are the highest rated books?
```{r}
books %>% 
  slice_max(average_rating, n = 5)
```
observations: 
*since 22 entries all share 5 as the highest value, we get more than 5 returned
*Some entries are not books, and this is identified by "NOT A BOOK" in the 
author column
*all of the books with the maximum rating have little to no reviews, which means 
their rating is heavily weighted by a small minority of readers.
*It appears that a book with no ratings is defaulted to a rating of 5



maybe it is a better idea to find the highest rated books with a minimum of 100
ratings, that are indeed books and not FAKE_BOOKS(scandalous.scl).

```{r}
books_rated <- books %>% 
  mutate(ratings_count = if_else(ratings_count < 100, NA, ratings_count)) %>% 
  filter(!is.na(ratings_count))

  slice_max(books_rated, average_rating, n = 5)

```

Driving out the impostors 

```{r}
#purged <- books %>% 
 # mutate(authors = if_else(authors == "NOT A BOOK", NA, authors)) %>%
  #filter(!is.na(authors))

purged <- books %>% 
  filter(!authors == "NOT A BOOK")
impostors <- books %>% 
  filter(authors == "NOT A BOOK")

impostors
```





how many books in each language

```{r}
books %>% 
  group_by(language_code) %>% 
  summarise(num_of_books = n()) %>% 
  arrange(desc(num_of_books))

#books %>% 
#  count(language_code)
```

Do more recently reviewed books recieve a higher average rating?

```{r}

books_min1_rating <- books %>% 
  filter(ratings_count > 0)
# We start again with the min1_rating dataset
books_min1_rating %>% 
  select(title, authors, publication_date, average_rating) %>% 
  # lets focus on years only
  mutate(year = format(as.Date(books_min1_rating$publication_date,
                               format="%m/%d/%Y"), "%Y"),
                       .before = publication_date) %>% 
# Let's just create 2 groups, before 2000 is 'old' and younger than 2000 'new'
mutate(age = case_when(
  year <2000 ~ "old",
  year >=2000 ~ "young"
), .after = year) %>% 
 # filter(is.na(year)) # there are 2 books that have NA for year, but publication date is like normal?!
  group_by(age) %>% 
  summarise(average_rating = mean(average_rating))
  
```



Languages that JK Rowling has published in 

```{r}
books %>% 
  select(authors, publication_date, language_code) %>% 
  mutate(JK = str_detect(authors, "J.K. Rowling"), .after = authors) %>% 
  filter(JK == TRUE) -> jk_books
  mutate(year = format(as.Date(jk_books$publication_date,
                               format="%m/%d/%Y"), "%Y"),
                       .before = publication_date)
  #count(language_code)
  arrange(desc(publication_date))
```

