---
title: "Decision trees homework"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    css: ../../../styles.css
  pdf_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = "center")
```


<br>
In this homework we will create a decision tree to see which factors are useful in predicting whether or not a passenger on the titanic will survive.  


Run the code below before you begin: 


```{r, warning = FALSE, message = FALSE}
library(rpart)
library(rpart.plot)
library(tidyverse)

library(tidyverse)
titanic_set <- read_csv('data/titanic_decision_tree_data.csv')

shuffle_index <- sample(1:nrow(titanic_set))

# shuffle the data so class order isn't in order - need this for training/testing split later on 
titanic_set <- titanic_set[shuffle_index, ]
```

<br>

**Data Dictionary**

  * **sex**: Biological Sex, male or female  
  * **age_status**: adult or child (child defined as under 16)  
  * **class** : Ticket class, 1 = 1st (Upper class), 2 = 2nd (Middle Class), 3 = 3rd (Lower Class)    
  * **port_embarkation**: C = Cherbourg, Q = Queenstown, S = Southampton  
  * **sibsp** : number of siblings / spouses aboard the Titanic   
  * **parch**: number of parents / children aboard the Titanic. Some children travelled only with a nanny, therefore parch=0 for them. 
  * **survived_flag** : did they survive, 0 = No, 1 = Yes  



# MVP 


## Question 1  

<br> 
Cleaning up the data is always the first step. Do the following: 

  * Take only observations which have a `survived` flag (i.e. that aren't missing)  
  * Turn your important variables into factors (sex, survived, pclass, embarkation)  
  * Create an `age_status` variable which groups individuals under (and including) 16 years of age into a category called "child" category and those over 16 into a category called "adult".  
  * Drop the NA  
  * Drop any variables you don't need (`X1`, `passenger_id`, `name`, `ticket`, `far`, `cabin`)  

If you need help doing this, the code is below, but please try it yourself first so you can learn!


```{r}
titanic_clean <- titanic_set %>% 
  filter(!is.na(survived)) %>% 
  mutate(sex = as.factor(sex),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower","Middle","Upper")),
         age_status = as.factor(if_else(age <= 16, "child", "adult")),
         embarked = str_to_lower(embarked),
         embarked = factor(embarked, c("c","q","s"), c("Cherbourg", "Queenstown", "Southampton")),
         survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes"))
         ) %>% 
    select(sex, age_status, class, embarked, sib_sp, parch, survived_flag) %>%
  na.omit()
```

```{r}
skimr::skim(titanic_clean)
```





<br>
<details>
<summary>**Data Cleaning Code** </summary>
<br>

```{r}
titanic_clean <- titanic_set %>%
  filter(survived %in% c(0,1)) %>%
# Convert to factor level
	mutate(sex = as.factor(sex), 
	       age_status = as.factor(if_else(age <= 16, "child", "adult")),
         class = factor(pclass, levels = c(3,2,1), labels = c("Lower", "Middle", "Upper")), 
	       survived_flag = factor(survived, levels = c(0,1), labels = c("No", "Yes")), 
	       port_embarkation = as.factor(embarked)) %>%
  select(sex, age_status, class, port_embarkation, sib_sp, parch, survived_flag) %>%
  na.omit()
```
</details>


<br>

## Question 2  

<br> 
Have a look at your data and create some plots to ensure you know what you're working with before you begin. Write a summary of what you have found in your plots. Which variables do you think might be useful to predict whether or not people are going to die? Knowing this before you start is the best way to have a sanity check that your model is doing a good job.  

<br>

```{r, message=FALSE}
library(GGally)
ggpairs(titanic_clean)
```
initial look makes it seem like class and sex a big impact 



## Question 3  

<br> 
Now you can start to build your model. Create your testing and training set using an appropriate split. Check you have balanced sets. Write down why you chose the split you did and produce output tables to show whether or not it is balanced. [**Extra** - if you want to force balanced testing and training sets, have a look at the `stratified()` function in package `splitstackshape` (you can specify multiple variables to stratify on by passing a vector of variable names to the `group` argument, and get back testing and training sets with argument `bothSets = TRUE`)]



```{r}
test_id <- sample(1:nrow(titanic_clean), 71)

titanic_test <- titanic_clean[test_id,]
titanic_train <- titanic_clean[-test_id,]
```

```{r}
titanic_test %>% 
  janitor::tabyl(survived_flag)
```

```{r}
titanic_train %>% 
  janitor::tabyl(survived_flag)
```

not super similair but close enough for now

## Question 4      

<br> 
Create your decision tree to try and predict survival probability using an appropriate method, and create a decision tree plot.

```{r}

# make the tree

titanic_fit <- rpart(
  formula = survived_flag ~ . ,
  data = titanic_train,
  method = "class"             # for categorical since we have did and didn't survive
)


# plot the tree

rpart.plot(titanic_fit,
           yesno = 2, # yes no at all splits
           type = 2, # dictates where conditions lie at each node
           fallen.leaves = TRUE, # brings all leaves to bottom
           faclen = 6,           # how many letters is each factor name allowed
           digits = 4,           # how many decimals is a prob reported in
           split.border.col = 1  # colour of the outline
           )
```




## Question 5    

<br> 
Write down what this tells you, in detail. What variables are important? What does each node tell you? Who has the highest chance of surviving? Who has the lowest? Provide as much detail as you can.    


the base chance of survival is 0.41

the lowest chance of survival is 0.21, which is determined being a man
the highest is 0.94 if you are an upper/middle class woman

the women who embarked at queenstown or southampton and had 1 or more siblings have the lowest female 
survival rate at 0.30

<br>

## Question 6     

<br>  
Test and add your predictions to your data. Create a confusion matrix. Write down in detail what this tells you for this specific dataset.  


```{r}
titanic_test_pred <- titanic_test %>% 
  add_predictions(titanic_fit, type = "class")

conf_mat(titanic_test_pred, truth = survived_flag, estimate = pred)
```

it looks to have a much higher specificity than sensitivity as it is picking up a large proportion of the
true negatives but a fairly low proportion of the positives, barely over two thirds.

```{r}
sensitivity(titanic_test_pred, truth = survived_flag, estimate = pred)
specificity(titanic_test_pred, truth = survived_flag, estimate = pred)
```

weirdly this seems flipped and I'm not sure why given that the confusion matrix and the functions were 
given the same data.

# Extension  

See how a `ranger()` random forest classifier compares with a single decision tree in terms of performance. Can you tune the values of the `mtry`, `splitrule` and `min.node.size` hyperparameters? Which variables in the dataset turn out to be most important for your best model? The `Kappa` metric might be the best one to focus on if you want to improve performance for an imbalanced data set. Do some research on the definition of `Kappa` before you start.

We provide the code in the dropdown below if you get stuck, but still want to play around with this (note that run time can be up to 5-10 mins for the tuning). **Save your notebook before you begin** in case you need to force quit your session!

<br>
<details>
<summary>**Code**</summary>

```{r, eval=FALSE}
library(ranger)

control <- trainControl(
  method = "repeatedcv", 
  number = 5, 
  repeats = 10
)

tune_grid = expand.grid(
  mtry = 1:6,
  splitrule = c("gini", "extratrees"),
  min.node.size = c(1, 3, 5)
)
```

```{r, eval=FALSE}
rf_tune <- train(
  survived_flag ~ ., 
  data = titanic_train, 
  method = "ranger",
  metric = "Kappa",
  num.trees = 1000,
  importance = "impurity",
  tuneGrid = tune_grid, 
  trControl = control
)

plot(rf_tune)
rf_tune
```
</details>
<br>

