---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```


1
```{r}
phones <- read_csv("data/20190928-items.csv") %>% 
  janitor::clean_names()

head(phones)
```




2
```{r}
phones %>% 
  count(brand) %>% 
  slice_max(n, n = 5)
```
samsung is packing mad phones right now 




```{r}
sam_phone <- phones %>% 
  filter(brand == "Samsung")
```




3
```{r}
sam_phone %>% 
  ggplot() +
  aes(x = rating) +
  geom_histogram(bins = 30,aes(y = after_stat(density))) +
   stat_function(fun = dnorm,
                args = list(
                  mean = mean(sam_phone$rating),
                  sd = sd(sam_phone$rating)
                ))
```

while the symmetry and centers of the data line up, there are clear outliers around 1,2 and 5 
that severely break from the normal distribution, as well as a much higher centre presented in
the data than in the normal curve. while the approximation is decent there may be better
distributions to represent the data


4.
```{r}
sam_phone %>% 
  mutate(z_rat_scale = scale(rating)) %>% 
  filter(z_rat_scale <= 1 & z_rat_scale >= -1) %>% 
  nrow()/nrow(sam_phone)
```

```{r}
sam_phone %>% 
  mutate(z_rat_scale = scale(rating)) %>% 
  filter(z_rat_scale <= 2 & z_rat_scale >= -2) %>% 
  nrow()/nrow(sam_phone)
```

```{r}
sam_phone %>% 
  mutate(z_rat_scale = scale(rating)) %>% 
  filter(z_rat_scale <= 3 & z_rat_scale >= -3) %>% 
  nrow()/nrow(sam_phone)
```

since almost 80% of the data is captured in the first sd dev this is not a prefect fit and
a different approximation should be considered.

```{r}
std_s_phone <- sam_phone %>% 
  mutate(z_rat_scale = scale(rating))


qqnorm(std_s_phone$z_rat_scale) 
  qqline(dnorm(100))
```

something is going crazy here qq line hates me