---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
```


```{r}
ames <- read_csv("data/ames.csv") %>% 
  janitor::clean_names()
```

```{r}
ames %>% 
  ggplot() +
  aes(lot_area) +
  geom_histogram()
```

clearly there are some extreme outliers in the data that lie well beyond the 99th percentile of 
the data that are skewing thingsto an extreme


```{r}
ames %>% 
  filter(lot_area < 30000) %>% 
  ggplot(aes(x = lot_area)) +
  geom_histogram(bins = 20,
                 aes(y = after_stat(density)),
                  fill = "springgreen4",
                 col = "white",
                 # after stat super important
                ) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = mean(ames$lot_area),
      sd = sd(ames$lot_area)
    ),
    col = "darkgreen"
  )
```

even with adjustment for outliers the peak seems very steam and the taper greater than it should 
be for a normal distribution


```{r}
infer_resample <- ames %>% 
  filter(lot_area < 30000) %>% 
  specify(response = lot_area) %>% 
  generate(reps = 5000, type = "bootstrap") %>% #
  calculate(stat = "mean") #statistic of interest for each resample

infer_resample
```

```{r}
infer_resample %>% 
  ggplot() +
  aes(stat) +
  geom_histogram()
```

central limit theorem still works

```{r}
infer_ci_95 <- infer_resample %>% 
  get_ci(level = 0.95, type = "percentile")

infer_ci_95
```

```{r}
infer_resample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_95)
```


```{r}
infer_ci_99 <- infer_resample %>% 
  get_ci(level = 0.99, type = "percentile")

infer_ci_99
```

```{r}
infer_resample %>% 
  visualise(bins = 30) +
  shade_ci(endpoints = infer_ci_99)
```

the new interval is broader since, in trying to be more certain of the placement of our mean, we have widened the number of options 

```{r}
  mean(infer_resample$stat)
```

badabing badaboom