---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
data("msleep")
```

1.

H0: the mean sleep time of all animals in the sample is the same as the sleep time of the 
    jabberwokie
    
H1: there is a difference in the sleep time of the mean sleep time of all animals in the sample
    and the sleep of the jabberwockie
    



```{r}
sleep_times <- msleep %>% 
  select(sleep_total)
```


```{r}
obs_stat <- sleep_times %>% 
  summarise(mean(sleep_total)) %>% 
  pull()
```



```{r}
null_distribution <- sleep_times %>% 
  specify(response = sleep_total) %>% 
  hypothesize(null = "point", mu = 7) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

null_distribution
```

```{r}
null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = obs_stat, direction = "both")
```



```{r}
null_distribution %>%
  get_p_value(obs_stat = obs_stat, direction = "both")
```

pval is less than 0.00001 so we have evidence at the 99% confidence level that the 
jabberwockie average sleep time differs from the mean sleep time of the 83 listed animals.




2.

H0: omnivores have the same mean sleep time or lower than herbivores

    µo ≤ µh

H1: omnivores have a longer mean sleep time than herbivores

    µo > µh


```{r}
vore <- msleep %>% 
  filter(vore == "herbi"|vore == "omni") %>% 
  select(vore, sleep_total)
```


```{r}
null_distribution_vore <- vore %>% 
  specify(sleep_total ~ vore) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>% 
  calculate(stat = "diff in means", order = c("omni", "herbi"))

null_distribution_vore
```




```{r}
obs_diff_in_mean <- vore %>% 
  filter(vore == "omni") %>% 
  summarise(mean(sleep_total)) -
  vore %>% 
  filter(vore == "herbi") %>% 
  summarise(mean(sleep_total)) %>% 
  pull()
  
```


```{r}
null_distribution_vore %>% 
  visualise() +
  shade_p_value(obs_stat = obs_diff_in_mean, direction = "right")
```

```{r}
null_distribution_vore %>% 
  get_p_value(obs_stat = obs_diff_in_mean, direction = "right")
```

at the 95% significance level there is not enough evidence to reject the null hypothesis,
that there is no significant difference between the mean sleep times of herbivores and omnivores







3.

H0: is the proportion of domesticated animals compared to all animals in the sample is lower 
    than or equal to 0.05
    
    prop(domestic) ≤ 0.05
    
H0: is the proportion of domesticated animals compared to all animals in the sample is greater 
    than 0.05
    
    prop(domestic) > 0.05
    
    


assuming NAs are not domesticated as they would be well documented, so FALSE

```{r}
is_domestic <- msleep %>% 
  select(conservation) %>% 
  mutate(na_be_gone = if_else(is.na(conservation), "meep", conservation),
         is_domestic = na_be_gone == "domesticated")

dom_prop <- sum(is_domestic$is_domestic)/nrow(is_domestic)
```


```{r}
null_prop <- is_domestic %>% 
  specify(response = is_domestic, success = "TRUE") %>% 
  hypothesize(null = "point", p = 0.05) %>% 
  generate(reps = 5000, type = "draw") %>% 
  calculate(stat = "prop")

head(null_prop)
```

```{r}
null_prop %>%
  visualise() +
  shade_p_value(obs_stat = dom_prop, direction = "right")
```

```{r}
null_prop %>%
  get_p_value(obs_stat = dom_prop, direction = "right")
```

There is evidence to suggest at the 98.97% confidence level that we can reject the null 
hypothesis that the proportion of domesticated animals compared to all animals in the sample is lower than or equal to 0.05.



1.2


1. 
type of test: point estimate test of proportion 

H0: 40% or fewer people in the town have heard of the coffee shop

    π ≤ 0.4

H1: more than 40% of people in the town have heard of the coffee shop

    π > 0.4
    



2.
type of test: independent two-sample test

H0: the placement of the website banner at the top of the page does not affect, or negatively
affects the CTR

    π top ≤ π else

H1: the banner being placed at the top of the page yields a higher CTR than the
    alternative banner placement
    
    π top > π else
    
    
    
3.
type of test: paired two-sample test

H0: there is no difference in the widths of parts from the start and end of the 
    week
    
    µ start = µ end
    
H1: there is a difference in the widths of parts from the start and end of the
    week
    
    µ start ≠ µ end
    
    


1.3

1. at the 95% confidence level there is not evidence to suggest that more than 40% of the 
    town has heard of the coffee shop
    
2. at the 99% confidence level there is enough evidence to reject the null hypothesis, that
    there is no difference or negative difference in CTR when the banner is at the top of the 
    webpage
    
3. at the 95% confidence level there is nowhere near enough evidence to suggest a difference in 
    widths of the parts manufactured at the start of the week compared to the end of the week
    
